### 2020-09-21 tex/results.tex
corrected the paper to suit comments from Reviewer 1, also updated this in the response to reviewers txt file

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{KeyGen} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:keyresults}
%\vspace{-.2cm}
\resizebox{\columnwidth}{!}{

%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

KeyGen-640 1x & 971 & 433 & 290 & 1/0 & 191 & 59 \\
KeyGen-640 4x & 1174 & 781 & 355 & 4/0 & 185 & 226 \\
KeyGen-640 8x & 1679 & 1570 & 532 & 8/0 & 182 & 445 \\
KeyGen-640 16x & 2587 & 2994 & 855 & 16/0 & 172 & 840 \\ \hline \Tstrut
KeyGen-640 \cite{howe2018standard} & 3771 & 1800 & 1035 & 1/6 & 167 & 51 \\ \hline \Tstrut

KeyGen-976 1x & 1243 & 441 & 362 & 1/0 & 189 & 25 \\
KeyGen-976 4x & 1458 & 792 & 440 & 4/0 & 184 & 97 \\
KeyGen-976 8x & 1967 & 1576 & 617 & 8/0 & 178 & 187 \\
KeyGen-976 16x & 2869 & 3000 & 908 & 16/0 & 169 & 355 \\ \hline \Tstrut
KeyGen-976 \cite{howe2018standard} & 7139 & 1800 & 1939 & 1/8 & 167 & 22 \\ \hline \Tstrut

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Encapsulation} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:encapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\resizebox{\columnwidth}{!}{

Encaps-640 1x & 4246 & 2131 & 1180 & 1/0 & 190 & 58 \\
Encaps-640 4x & 4620 & 2552 & 1338 & 4/0 & 183 & 221 \\
Encaps-640 8x & 5155 & 3356 & 1485 & 8/0 & 177 & 427 \\
Encaps-640 16x & 5796 & 4694 & 1692 & 16/0 & 171 & 825 \\ \hline \Tstrut
Encaps-640 \cite{howe2018standard} & 6745 & 3528 & 1855 & 1/11 & 167 & 51 \\ \hline \Tstrut

Encaps-976 1x & 4650 & 2118 & 1272 & 1/0 & 187 & 25 \\
Encaps-976 4x & 4996 & 2611 & 1455 & 4/0 & 180 & 94 \\
Encaps-976 8x & 5562 & 3349 & 1608 & 8/0 & 175 & 183 \\
Encaps-976 16x & 6188 & 4678 & 1782 & 16/0 & 168 & 350 \\ \hline \Tstrut

Encaps-976 \cite{howe2018standard} & 7209 & 3537 & 1985 & 1/16 & 167 & 22 \\ \hline \Tstrut

@@

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Decapsulation} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA. Asterisk (*) denotes designs that used BRAM.}\label{tab:decapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\resizebox{\columnwidth}{!}{

Decaps-640 1x & 10518 & 2299 & 2933 & 1/0 & 190 & 57 \\
Decaps-640 4x & 11581 & 2818 & 3424 & 4/0 & 174 & 208 \\
Decaps-640 8x & 13128 & 3737 & 3710 & 8/0 & 164 & 391 \\
Decaps-640 16x & 14528 & 5335 & 4020 & 16/0 & 160 & 763 \\ \hline \Tstrut
*Decaps-640 1x & 4466 & 2152 & 1254 & 1/12.5 & 162 & 49 \\
*Decaps-640 4x & 4841 & 2661 & 1345 & 4/12.5 & 161 & 192 \\
*Decaps-640 8x & 5476 & 3479 & 1558 & 8/12.5 & 156 & 372 \\
*Decaps-640 16x & 6881 & 5081 & 1947 & 16/12.5 & 149 & 710 \\ \hline \Tstrut

Decaps-640 \cite{howe2018standard} & 7220 & 3549 & 1992 & 1/16 & 162 & 49 \\ \hline \Tstrut

Decaps-976 1x & 14217 & 2295 & 3956 & 1/0 & 188 & 25 \\
Decaps-976 4x & 16234 & 2853 & 4648 & 4/0 & 170 & 88 \\
Decaps-976 8x & 17451 & 3687 & 4985 & 8/0 & 161 & 167 \\
Decaps-976 16x & 18960 & 5285 & 5274 & 16/0 & 157 & 325 \\ \hline \Tstrut
*Decaps-976 1x & 4888 & 2153 & 1390 & 1/19 & 162 & 21 \\
*Decaps-976 4x & 5259 & 2662 & 1450 & 4/19 & 160 & 83 \\
*Decaps-976 8x & 5888 & 3490 & 1615 & 8/19 & 155 & 161 \\
*Decaps-976 16x & 7213 & 5087 & 2042 & 16/19 & 148 & 306 \\ \hline \Tstrut

Decaps-976 \cite{howe2018standard} & 7773 & 3559 & 2158 & 1/24 & 162 & 21 \\ \hline \Tstrut

@@

By changing our PRNG source and parallelising the most computationally heaving components in FrodoKEM we have shown significant improvements in FPGA area consumption and throughput performance compared to the previous works. For instance, comparing to FrodoKEM module~\cite{howe2018standard} (that is using one multiplier) we reduce slice consumption by 3.6x and 5.4x for key generation and 1.6x for encapsulation, all whilst not requiring any BRAM, whereas previous results utilize BRAM. For decapsulation, we save between 1.6x and 2.6x slices when BRAM is used and gain in slice counts by 1.5x and 1.1x if BRAM is not used. This increase is expected since more than half of this is due to storage otherwise used in BRAM.

Since the majority of our proposed designs operate without BRAM, we are able to attain a higher frequency than previous works. Overall our throughput outperforms previous \emph{comparable} results, by factors between 1.13x and 1.19x~\cite{howe2018standard}. Moreover, whilst maintaining less area consumption than previous research, we are able to increase the amount of parallel multipliers. As a result, we can achieve up to 840 key generations per second (a 16.5x increase), 825 encapsulations per second (a 16.2x increase), and 710 operations per second (a 15.6x increase). We also maintain the constant run-time which the previous implementation attains, as well as implementing first-order masking during decapsulation. The masking is also done using parallel multiplication and thus does not affect the run-time of the decapsulation module. The clock cycle counts for each module are easy to calculate; key generation requires $ (n^2\bar{n}) / k$ clocks, encapsulation requires $ (n^2\bar{n} + \bar{n}^2n)/k $ clocks, and decapsulation requires $(n^2\bar{n} + 2\bar{n}^2n)/k$ clocks, for dimensions $n=640$ or 976, $\bar{n}=8$, and $k$ referring to the number of parallel multipliers used.

>>>>

\begin{table*}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{KeyGen} designs, using 1, 4, 8, and 16 parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:keyresults}
%\vspace{-.2cm}
%\resizebox{\columnwidth}{!}{

%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r r r r r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ & Area$\times$Time \\
Protocol &&&& BRAM && Sec & (Slices$\times$Secs) \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

KeyGen-640 1x & 971 & 433 & 290 & 1/0 & 191 & 59 & 4.92 \\
KeyGen-640 4x & 1174 & 781 & 355 & 4/0 & 185 & 226 & 1.58 \\
KeyGen-640 8x & 1679 & 1570 & 532 & 8/0 & 182 & 445  & 1.20 \\
KeyGen-640 16x & 2587 & 2994 & 855 & 16/0 & 172 & 840  & 1.02 \\ \hline \Tstrut
KeyGen-640 \cite{howe2018standard} & 3771 & 1800 & 1035 & 1/6 & 167 & 51 & 20.29 \\ \hline \Tstrut

KeyGen-976 1x & 1243 & 441 & 362 & 1/0 & 189 & 25 & 14.48 \\
KeyGen-976 4x & 1458 & 792 & 440 & 4/0 & 184 & 97 & 4.54 \\
KeyGen-976 8x & 1967 & 1576 & 617 & 8/0 & 178 & 187 & 3.30 \\
KeyGen-976 16x & 2869 & 3000 & 908 & 16/0 & 169 & 355 & 2.56 \\ \hline \Tstrut
KeyGen-976 \cite{howe2018standard} & 7139 & 1800 & 1939 & 1/8 & 167 & 22 & 88.14 \\ \hline \Tstrut

\end{tabular}%}
\end{table*}

\begin{table*}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Encapsulation} designs, using 1, 4, 8, and 16 parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:encapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
%\resizebox{\columnwidth}{!}{

\begin{tabular}{l r r r r r r r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ & Area$\times$Time \\
Protocol &&&& BRAM && Sec & (Slices$\times$Secs) \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

Encaps-640 1x & 4246 & 2131 & 1180 & 1/0 & 190 & 58 & 20.34 \\
Encaps-640 4x & 4620 & 2552 & 1338 & 4/0 & 183 & 221 & 6.05 \\
Encaps-640 8x & 5155 & 3356 & 1485 & 8/0 & 177 & 427 & 3.48 \\
Encaps-640 16x & 5796 & 4694 & 1692 & 16/0 & 171 & 825 & 2.05 \\ \hline \Tstrut
Encaps-640 \cite{howe2018standard} & 6745 & 3528 & 1855 & 1/11 & 167 & 51 & 36.37 \\ \hline \Tstrut

Encaps-976 1x & 4650 & 2118 & 1272 & 1/0 & 187 & 25 & 50.88 \\
Encaps-976 4x & 4996 & 2611 & 1455 & 4/0 & 180 & 94 & 15.47 \\
Encaps-976 8x & 5562 & 3349 & 1608 & 8/0 & 175 & 183 & 8.79 \\
Encaps-976 16x & 6188 & 4678 & 1782 & 16/0 & 168 & 350 & 5.09 \\ \hline \Tstrut

Encaps-976 \cite{howe2018standard} & 7209 & 3537 & 1985 & 1/16 & 167 & 22 & 90.22 \\ \hline \Tstrut

\end{tabular}%}
\end{table*}

@@

\begin{table*}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Decapsulation} designs, using 1, 4, 8, and 16 parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA. Asterisk (*) denotes designs that used BRAM.}\label{tab:decapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
%\resizebox{\columnwidth}{!}{

\begin{tabular}{l r r r r r r r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ & Area$\times$Time \\
Protocol &&&& BRAM && Sec & (Slices$\times$Secs) \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

Decaps-640 1x & 10518 & 2299 & 2933 & 1/0 & 190 & 57 & 51.46 \\
Decaps-640 4x & 11581 & 2818 & 3424 & 4/0 & 174 & 208 & 16.46 \\
Decaps-640 8x & 13128 & 3737 & 3710 & 8/0 & 164 & 391 & 9.49 \\
Decaps-640 16x & 14528 & 5335 & 4020 & 16/0 & 160 & 763 & 5.27 \\ \hline \Tstrut
*Decaps-640 1x & 4466 & 2152 & 1254 & 1/12.5 & 162 & 49 & 25.59 \\
*Decaps-640 4x & 4841 & 2661 & 1345 & 4/12.5 & 161 & 192 & 7.00 \\
*Decaps-640 8x & 5476 & 3479 & 1558 & 8/12.5 & 156 & 372 & 4.19 \\
*Decaps-640 16x & 6881 & 5081 & 1947 & 16/12.5 & 149 & 710 & 2.74 \\ \hline \Tstrut

Decaps-640 \cite{howe2018standard} & 7220 & 3549 & 1992 & 1/16 & 162 & 49 & 40.65 \\ \hline \Tstrut

Decaps-976 1x & 14217 & 2295 & 3956 & 1/0 & 188 & 25 & 158.24 \\
Decaps-976 4x & 16234 & 2853 & 4648 & 4/0 & 170 & 88 & 52.82 \\
Decaps-976 8x & 17451 & 3687 & 4985 & 8/0 & 161 & 167 & 29.85 \\
Decaps-976 16x & 18960 & 5285 & 5274 & 16/0 & 157 & 325  & 16.23 \\ \hline \Tstrut
*Decaps-976 1x & 4888 & 2153 & 1390 & 1/19 & 162 & 21 & 66.19 \\
*Decaps-976 4x & 5259 & 2662 & 1450 & 4/19 & 160 & 83 & 17.47 \\
*Decaps-976 8x & 5888 & 3490 & 1615 & 8/19 & 155 & 161 & 10.03 \\
*Decaps-976 16x & 7213 & 5087 & 2042 & 16/19 & 148 & 306 & 6.67 \\ \hline \Tstrut

Decaps-976 \cite{howe2018standard} & 7773 & 3559 & 2158 & 1/24 & 162 & 21 & 102.76 \\ \hline \Tstrut

\end{tabular}%}
\end{table*}

@@

By changing our PRNG source and parallelising the most computationally heaving components in FrodoKEM we have shown significant improvements in FPGA area consumption and throughput performance compared to the previous works. For instance, comparing to FrodoKEM module~\cite{howe2018standard} (that is using one multiplier) we reduce slice consumption by 3.6x and 5.4x for key generation and 1.6x for encapsulation, all whilst not requiring any BRAM, whereas previous results utilize BRAM. For decapsulation, we decrease the amount of slices used between 1.6x and 2.6x when BRAM is used and similarly decrease slice counts by 1.5x and 1.1x when BRAM is not used. These savings are expected since more than half of this is due to storage otherwise used in BRAM.

Tables \ref{tab:keyresults}, \ref{tab:encapsresults}, and \ref{tab:decapsresults} also contain a metric to analyse the area-time efficiency of the proposed designs. This metric takes into account the hardware design's utilisation of slices (i.e., not BRAM) and the time taken (in this case, seconds) for a full key generation, encapsulation, or decapsulation operation to complete. There is a common trend when analysing these results; the hardware designs become significantly more performant when the number of parallel multipliers are increase. We also see this in the increase in throughput performance in Figure \ref{fig:hw_line}. Moreover, we can use this metric to compare with previous work by Howe et al. \cite{howe2018standard} to see that in all cases, parallelising results provide significant speed-ups; up to 35x improvement for key generation.

Since the majority of our proposed designs operate without BRAM\footnote{We ensure BRAM is not inferred in our designs by setting \texttt{-max\_bram} to zero for synthesis in Vivado.}, we are able to attain a higher frequency than previous works. Overall our throughput outperforms previous \emph{comparable} results, by factors between 1.13x and 1.19x~\cite{howe2018standard}. Moreover, whilst maintaining less area consumption than previous research, we are able to increase the amount of parallel multipliers. As a result, we can achieve up to 840 key generations per second (a 16.5x increase), 825 encapsulations per second (a 16.2x increase), and 710 operations per second (a 15.6x increase). We also maintain the constant run-time which the previous implementation attains, as well as implementing first-order masking during decapsulation. The masking is also done using parallel multiplication and thus does not affect the run-time of the decapsulation module. The clock cycle counts for each module are easy to calculate; key generation requires $ (n^2\bar{n}) / k$ clocks, encapsulation requires $ (n^2\bar{n} + \bar{n}^2n)/k $ clocks, and decapsulation requires $(n^2\bar{n} + 2\bar{n}^2n)/k$ clocks, for dimensions $n=640$ or 976, $\bar{n}=8$, and $k$ referring to the number of parallel multipliers used.
